%
% Template for Doctoral Theses at Uppsala 
% University. The template is based on    
% the layout and typography used for      
% dissertations in the Acta Universitatis 
% Upsaliensis series                      
% Ver 5.2 - 2012-08-08                  
% Latest version available at:            
%   http://ub.uu.se/thesistemplate            
%                                         
% Support: Wolmar Nyberg Akerstrom        
% Thesis Production           
% Uppsala University Library              
% avhandling@ub.uu.se                          
%                                         
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass{UUThesisTemplate}

% Package to determine wether XeTeX is used
\usepackage{ifxetex}
\usepackage{mathtools}
\newcommand\isdef{\stackrel{\mathclap{\tiny\normalfont\mbox{def}}}{=}}
\ifxetex
	% XeTeX specific packages and settings
	% Language, diacritics and hyphenation
	\usepackage[babelshorthands]{polyglossia}
	\setmainlanguage{english}
	\setotherlanguages{swedish}

	% Font settings
	\setmainfont{Times New Roman}
	\setromanfont{Times New Roman}
	\setsansfont{Arial}
	\setmonofont{Courier New}
\else
	% Plain LaTeX specific packages and settings
	% Language, diacritics and hyphenation
    % Use English and Swedish languages. 
	\usepackage[swedish,english]{babel} 

	% Font settings
	\usepackage{type1cm}
	\usepackage[latin1]{inputenc}
	\usepackage[T1]{fontenc}
	\usepackage{mathptmx}
	
	% Enable scaling of images on import
	\usepackage{graphicx}
\fi


% Tables
\usepackage{booktabs}
\usepackage{tabularx}

% Document links and bookmarks
\usepackage{hyperref} 

% Numbering of headings down to the subsection level
\numberingdepth{section}

% Including headings down to the subsection level in contents
\contentsdepth{section}


% Uncomment to use a custom abstract dummy text
%\abstractdummy{
%	\begin{abstract}
%		Please use no more than 300 words and avoid mathematics or complex script.
%	\end{abstract}
%}


\begin{document}
\frontmatter
    % Creates the front matter (title page(s), abstract, list of papers)
    % for either a Comprehensive Summary or a Monograph.
    % Authors of Comprehensive Summaries use this front matter 
    \frontmatterCS 
    % Monograph authors use this front matter 
    %\frontmatterMonograph 
 
   % Optional dedication
   \dedication{Dedicated to our new Life: Emmanuel and Mathis}
 
    % Environment used to create a list of papers
    \begin{listofpapers}
    	\item Imaging single cells in a beam of live cyanobacteria. %\label{ImCell}
        \item Open dataset of live cyanobacterial cells imaged using an X-ray laser. %\label{DataCell}
        \item RedFlamingo: Suite for automated classification of diffraction patterns. %\label{RefFlamingo}
        \item Template-based classification of diffraction patterns. %\label{TempClass}
        \item Open dataset of RDV particles. %\label{DataRDV}
    \end{listofpapers}
    
    \begin{listofsupportingpapers}
	\item G. van der Schot and A.M.J.J. Bonvin. Performance of the WeNMR CS-Rosetta3 web server in CASD-NMR. Journal of Biomolecular NMR, 62(4),497-502, 2015.	
	\item G. van der Schot \textit{et al.} Improving 3D structure prediction from chemical shift data. Journal of biomolecular NMR, 57(1):27-35,2013.
	\item T.A. Wassenaar \textit{et al.} WeNMR: Structural Biology on the Grid. Journal of Grid Computing, 10(4):747-767, 2012.
	\item A. Rosato    \textit{et al.} Blind testing of routine, fully automated determination of protein structures from NMR data. Structure, 20(2):227-236, 2012.
	\item M. Vendruscolo \textit{et al.} Protein structure
determination using chemical shifts, NMR in Mechanistic Systems Biology, Chapter 10, 107-110, 2009.
 	\item A. Rosato    \textit{et al.} CASD-NMR: critical assessment of automated structure determination by NMR. Nature Methods, 6(9):625-626, 2009.
 	\item R.P. Kurta   \textit{et al.} Phys. Rev. Lett. 119, 158102, 2017.
	\item H.K.N. Reddy \textit{et al.} Coherent soft X$-$ray diffraction imaging of coliphage PR772 at the Linac coherent light source. Scientific Data, 4:170079, 2017.
	\item  B.J. Daurer \textit{et al.} Experimental strategies for imaging bioparticles with femtosecond hard X-ray pulses. IUCrJ, 4(3):252-262, 2017.
	\item M.F. Hantke  \textit{et al.} A data set from flash X-ray imaging of carboxysomes. Scientific data, 3:160061, aug 2016.
	\item A. Munke     \textit{et al.} Coherent diffraction of single Rice Dwarf virus particles using hard X-rays at the Linac Coherent Light Source. Scientific data, 3:160064, 2016.
	\item T. Ekeberg   \textit{et al.} Three-Dimensional Reconstruction of the Giant Mimivirus Particle with an X-Ray Free-Electron Laser. Physical Review Letters, 114(9):098102, 2015.
	\item M.F. Hantke  \textit{et al.} High-throughput imaging of heterogeneous cell organelles with an X-ray laser. Nature Photonics, 8(12):943-949, 2014.
	\item A.V. Martin  \textit{et al.} Noise-robust coherent diffractive imaging with a single diffraction pattern. Optics Express, 20(15):16650, 2012.	
    \end{listofsupportingpapers}
    \begingroup
        % To adjust the indentation in your table of contents, uncomment and enter the widest numbers for each level
        %  E.g.  \settocnumwidth{widest chapter number}{widest section number}{widest subsection number}...{...}
       %  \settocnumwidth{5}{4}{5}{3}{3}{3}
        \tableofcontents
    \endgroup
    
    % Optional tables
    %\listoftables
    %\listoffigures

\mainmatter
    
    % Include your chapters here.
    %\input{Introduction.tex}
    \input{Chapter_01_Motivation.tex}
    \input{Chapter_02_InteractionLightAndMatter.tex}
    \input{Chapter_03_GenerationXrayXFEL.tex}
    \input{Chapter_04_SampleInjection.tex}
    \input{Chapter_05_SignalDetection.tex}
    \input{Chapter_06_DataAnalysis.tex}
    \input{Chapter_07_Reconstruction3DObject.tex}
    \input{Chapter_08_ImageClassification.tex}
    \input{Chapter_09_Results.tex}
    %\input{Chapter_10_Outlook.tex}
	\input{Chapter_11_SammanfattningPaSvenska.tex}

\backmatter
    % References
    % No restriction is set to the reference styles
    % Save your references in References.bib
    \nocite{*} % Remove this for your own citations
    \bibliographystyle{plain}
    \bibliography{Thesis}

\end{document}